Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-23 journal/article.tex
S: Management support

The most prominent and clear success factor was having support from management.

@@

The formation and influence of agile communities had a significant impact on
transformation.

@@

* A success factor: Agile communities emerged
* Communities are commonly created in agile initiatives
[P3]

* There was an agile community which spawned eager followers
* The community shared experiences and advice
* The community emerged self-organized
[P12]

* Project managers were in a matrix structure
* The matrix enabled sharing of learnings and confirmation 
[P12]

* The organization is planning on establishing an agile CoP
[P30]

* The coaches built up an agile community
* There was online discussions, newsletters, and workshop events
[P41]

* The company has communities of practice, which are effective in raising awareness
  of engineering practices
[P42]

* The agile coach community is a driving force --> They achieved becomming a driving force
* The community created practices promoting the use of agile methods in the organization
[P47]

* A collective group is required to make chage in an organization
* Impediments may be too large for individuals to move
[P47]

S: Have an agile community

>>>>

% Management support in general

The most prominent and clear success factor was having support from management.
Numerous cases made it clear that management support is an absolute necessity
[P8, P18, P27, P31, P33, P36, P43, P47, P49].
This was reflected in statemets such as ``Adopting agile, or implementing any
significant change, requires an executive’s sincere support.'' [P44],
``Executive commitment was crucial to implementing massive change.'' [P16], and
``Having upper management engaged, supportive and visible is critical for
wholesale organization involvement with Scrum.'' [P11].

Managers were seen to be in a key role in making the change stick, as they had
the authority and power to remove impediments [P18]. Seffernick [P46] describes
how a number of people attempted to explain away the applicability of agile
methods, but the objections were overruled by the director's commitment to make
agile work. Management support was similarly needed when tight release schedules
had to be flexed in order to give room for the adoption process [P16, P27].
Favorable management decisions were also critical when additional resources were
allocated to training and coaching [P47].

Visible involvment of management was also reported to motivate and encourage
employees to adopt the new model [P40]. For instance, the CTO organized training
sessions personnally [P24], and the engineering VP frequently visited sprint
demos [P11]. When the corporate level support for the agile initiative was
showing teams adopted agile methods even spontaneously [P9].

There were a few suggestions on how to involve management better. Foremost, a
successful experience will likely rise the interest of management [P36].
Mencke [P33] suggests giving executives tasks related to the agile process,
so that they have better visibility of the new way of working.

% Educate management

In order to gain support for agile several cases highlighted the need to educate
managment [P8, P47].
Without education managers might make harmful interventions in the process, or
just stick to the old model [P16, P35, P46].
Managers not understanding the principles of agile were feeling left out with
the introduction of self organizing teams, which some times resulted in
backlashes [P6]. Providing proper training was reported to correct the
situation, and even create strong agile supporters in management [P6, P9].
Training also cleared misconceptions that management had [P29], and helped
create a consistent implementation of the agile model across the organization
[P11].

@@

@@
